\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage{markdown}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage[subtle]{savetrees}
\usepackage{verbatim}
\usepackage{blindtext}

\title{\vspace{-2cm} \textbf{Session 7 - Debug Session} \\ UCAS Program 2020}

\author{Chloe Lau}
\date{August 2020}

\begin{document}
\setlength{\parindent}{4ex}
\setlength{\parskip}{1em}

\maketitle

\section{Ah Well...}
"It's the last group seminar, oh no I still have many questions! I need help with university selection! Tell me more about university life! How do I strive through A Levels?"

This is why this is called a Debug Session, we will fix the problems with you! Bombard me with questions and I'm here to solve them:)

There is no general notes for this seminar, mostly questions by you, answered by me.

\section{Final Words}
It has been a pleasure to teach this cohort, and I am surprised by how many Computer Scientists CSFC is producing now, more than double of my year. I wish you all the best in your future endeavours, and good luck with your UCAS preparation.

To keep in contact after the course: you can find my details \href{https://chloelwt.com}{here}.

The repository for all of these \LaTeX{} notes will be up on my \href{https://github.com/chloelaucodes/ucas_program_notes}{GitHub}.

Hoping I will see some of you at Imperial in the near future!

Good luck and have fun with the interviews.

\setlength{\parindent}{0pt}
Cheers,\newline
Chloe x

\end{document}
